Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-08-26 manuscript/main.tex
updated ncsl results in manuscript

\begin{enumerate}
    \item Collect all urls returned by the bing search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
    \item Sample 50 urls
    \item Select bills that fulfill these three conditions:
        \begin{enumerate}
            \item The website is a NCSL table
            \item The table refers (at least in part) to legislation introduced in 2011 or later.             \item The table contains less than 100 individual bills. 
        \end{enumerate}
    \item Scrape all information from these tables
\end{enumerate}

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22
fulfilled the three criteria. From these 22 tables we constructed a dataset of
950 bills, of which we could match 704 to our bill database. For all bill pairs
that we do not have alignment scores for (i.e. the bills did not get matched by
the pre-selection algorithm) we assume a score of 0\footnote{If a bill is not selected in the pre-selection step, this means
that there are basically no matching sequences in this dyad.}.

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We see generally high precision---over 80\% with moderate
(higher than 50) to high alignment scores (about 3\% of bill-dyad alignment
scores fall into this category). When alignment scores are very high (over 100)
we see extremely high precision (1\% of bill-dyad alignment scores fall into
this category). Recall is generally low, but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a rare event ($3*10^{-4}$\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}. Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ncsl_prec_rec.png}
    \caption{Precision-Recall curve for classifying two bills being in the same
    ncsl table by thresholding the bill-dyad alignment score. The x axis
displays the threshold, the y axis represents precision and recall. The shaded
area in the background displays the frequency distribution of the alignment
scores. Note that the figure does not include alignments with score exactly 0.}
    \label{fig:ncsl_prec_rec}
\end{figure}

@@

In the following sections we present several analyses to assess this correlation. When we are generating the alignments the bills are split up into sections. We generate an alignment score for a bill dyad by first taking the logarithm and then summing over all section dyads of the bill dyad. The ideal point of the bill is derived from the ideal point of the primary bill sponsor. For bills with several primary sponsors we use the average of those sponsors' ideal points to obtain a single measure. Figure \ref{fig:ideology_quantile_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset. Each dot is a hexagonal tile, the color of the tile represents the number of dyads in that area. Two major observations can be made in this plot. First, the vast majority of alignment scores are close to zero. Second, the triangular shape of the distribution indicates the high precision - low recall character of the alignment score discussed above: few bills exhibit meaningful policy overlap with other bills, but in the region of lower ideological distance we observe a greater occurrence of positive outliers, which arise from significant policy overlap.

In order to investigate this pattern more closely, we additionally provide lines for quantile regressions in the Figure \ref{fig:ideology_quantile_plot}. Figure \ref{fig:quantile_regression} displays more details about these regression. Figure \ref{fig:ideology_plot} displays the distribution without the quantile regression lines. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap proposed by \citet{harden2011bootstrap}. We see that there is no relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases---especially above the 90th percentile, we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.}
    \label{fig:ideology_plot}
\end{figure}

>>>>

\begin{enumerate}
    \item Collect all urls returned by the web search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
    \item Sample 50 urls
    \item Select bills that fulfill these three conditions:
        \begin{enumerate}
            \item The website is a NCSL table
            \item The table refers (at least in part) to legislation introduced in 2011 or later.             \item The table contains less than 100 individual bills. 
        \end{enumerate}
    \item Scrape all information from these tables
\end{enumerate}

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22
fulfilled the three criteria. From these 22 tables we constructed a dataset of
950 bills, of which we could match 704 to our bill database\footnote{We
    additionally excluded one bill. Indiana 2012 HB1009
    (\url{www.in.gov/legislative/bills/2012/HE/HE1009.1.html}), which is a
    very long bill containing technical corrections to a large number of
    other bills. Due to this fact it contains a large number of sections that
produce a large outlier alignment when aggregated}. Since this is a
relatively low number of bills, we then calculate the complete set of pairwise
alignments for these bills. As described above, we split the
bills in sections, calculate the pairwise section alignments. This results in
approximately $10^7$ section-dyads. We then aggregate these section-dyads to the
bill-dyad level.

For this analysis we additionally employed the boilerplate adjustment strategy
described above\footnote{We plan to use boiler plate adjustment for all
    analyses. We are experimenting with the boiler plate removal on this
    analysis because the smaller size of the data. The final evaluation will be
    conducted on a held out data set of ncsl tables that is not included in the
current sample}. Before aggregating the alignments to the bill-dyad level, their
score is weighted by the inverse frequency of the alignment in the set of all
alignments for this analysis\footnote{The exact procedure is to compile the
matching elements of the two aligned sequences to a string that can then be
matched. This means that mismatches and gaps are ignored, since they would make
the alignment text unique.}. This results in down-weighting of alignments that occur too often to
be considered relevant policy language. Table
\ref{tab:expl_align_freq} displays some example alignments with very high and
very low frequency. From analysis of these frequencies we find that all alignments
that occur very frequent are indeed boilerplate. However, there are also still
many boilerplate alignments that occur infrequently. The currently employed
approach therefore improves the signal in the alignment score, but could be
further improved by matching and aggregating not only equal but also similar alignments (e.g. using another alignment
step or bag-of-words similarity measures).

\begin{table}[]
\centering
\caption{Example alignment text of comparable length occurring with high and low frequency.}
\label{tab:expl_align_freq}
\begin{tabular}{lll}
\hline
Frequency & Matched Alignment Text                           & Rank   \\
\hline
1         & to the treasurer of the county in which the      & 1      \\
1         & shall be for purposes of this                    & 1      \\
1         & of the higher education act of 1965              & 1      \\
...       & ...                                              & ...    \\
7089      & be it enacted by the legislature of the state of & 244747 \\
19349     & be it enacted by the of the state of             & 244840 \\
21100     & is amended to read as follows                    & 244847 \\
\hline
\end{tabular}
\end{table}

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We display the results for the alignment scores adjusted for
boilerplate (left panel) and the unweighted scores (right panel). We see
moderate to high precision --- 60\% - 100\% with moderate
(higher than 6) to high alignment scores (about 1\% or 2000 of bill-dyad alignment
scores fall into this category) for the adjusted scores. The
threshold-classification using the unweighted scores performs much worse. This
is due to the fact that some bills with large numbers of section have high
bill-dyad level alignment scores simply due to the fact that they have many
boilerplate alignments. These results indicate that down-weighting by inverse
frequency is a promising direction to take.

Recall is low at thresholds that produce reasonable precision (above 6), but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a relatively rare event (8\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}. Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.

\begin{figure}
\centering     %%% not \center
\subfigure[Precision recall curve for boilerplate adjusted
scores]{\label{fig:prec_rec_adj}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_adj.png}}
\subfigure[Precision recall curve for unweighted
scores]{\label{fig:prec_rec_old}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_old.png}}
\caption{Precision-Recall curve for classifying two bills being in the same
    ncsl table by thresholding the bill-dyad alignment score. The left panel displays the curve for the alignment scores weighted by the inverse frequency of the alignment, the left panel displays the curve for the unweighted scores. The x axis
displays the threshold, the y axis represents precision and recall. The shaded
area in the background displays the frequency distribution of the alignment
scores.}
\label{fig:ncsl_prec_rec}
\end{figure}

@@

In the following sections we present several analyses to assess this correlation. When we are generating the alignments the bills are split up into sections. We generate an alignment score for a bill dyad by first taking the logarithm and then summing over all section dyads of the bill dyad. The ideal point of the bill is derived from the ideal point of the primary bill sponsor. For bills with several primary sponsors we use the average of those sponsors' ideal points to obtain a single measure. Figure \ref{fig:ideology_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset. Each dot is a hexagonal tile, the color of the tile represents the number of dyads in that area. Two major observations can be made in this plot. First, the vast majority of alignment scores are close to zero. Second, the triangular shape of the distribution indicates the high precision - low recall character of the alignment score discussed above: few bills exhibit meaningful policy overlap with other bills, but in the region of lower ideological distance we observe a greater occurrence of positive outliers, which arise from significant policy overlap.

In order to investigate this pattern more closely, we additionally calculate
quantile regressions for the relationship between the alignment score and the
ideological distance. Figure \ref{fig:quantile_regression} displays the
coefficients from quantile regressions on a sequence of quantiles from the
median to the 0.995th quantile. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap proposed by \citet{harden2011bootstrap}. We see that there is no relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases---especially above the 90th percentile, we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.

\begin{figure}[ht!]i
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.}
    \label{fig:ideology_plot}
\end{figure}
